Deriving Multi-Headed Projective Dependency Parses \\ from Link Grammar Parses

### 2014-06-03 doc/LinksToDAG.tex
space hacking
my changes

The link grammar parses do differ in style from the single-headed CoNLL parses of the same English sentences.  They have !!!\% more edges overall.  Only !!!\% of the links match CoNLL arcs, and only !!!\% of the CoNLL arcs match links.
% DATA FOR THE ABOVE
% \begin{figure}[ht!]
%   \centering
%   \small
%   \input{figure/conll_analysis_arcs.tex}
%   \caption{Arcs that match links}
% \end{figure}
% 
% OLD
% Using the sentences of the dependency corpus as comparison, we find that the link parses do not wholly subsume dependency parses, and that the undirected links match roughly three fourths of the arcs in the conll dependency corpus. \todo{This is because...}

@@

We solved our ILP problem using the SCIP Optimization Suite \cite{achterberg2009scip}, encoding it using the ZIMPL language \cite{Koch2004}.  Our largest run took under an hour. \noteJH{A run of 10,000 sentences takes 3142 seconds (update in final version!)}  Detailed results from this run are included as Appendix~\ref{app:linktypes}.  On English, !!! of !!! link {\em types} allowed both directions, and only $\sum_{ij} s_{ij} = !!!$ of !!! link {\em tokens} required a disallowed direction via slack.
\input{figure/conll_analysis_sentences_multiheaded}of the English sentences and !!! of the Russian sentences had at least one multiheaded word.

>>>>

The link grammar parses do differ in style from the single-headed CoNLL parses of the same English sentences.  They have \input{figure/conll_analysis_edge_percent.tex}more edges overall.  Only \input{figure/conll_analysis_precision.tex}of the links match CoNLL arcs, and only \input{figure/conll_analysis_recall.tex}of the CoNLL arcs match links.
% DATA FOR THE ABOVE
% \begin{figure}[ht!]
%   \centering
%   \small
%   \input{figure/conll_analysis_arcs.tex}
%   \caption{Arcs that match links}
% \end{figure}
% 
% OLD
% Using the sentences of the dependency corpus as comparison, we find that the link parses do not wholly subsume dependency parses, and that the undirected links match roughly three fourths of the arcs in the conll dependency corpus. \todo{This is because...}

@@

We solved our ILP problem using the SCIP Optimization Suite \cite{achterberg2009scip}, encoding it using the ZIMPL language \cite{Koch2004}.  Our largest run took under an hour. \noteJH{A run of 10,000 sentences takes 3142 seconds (update in final version!)}  Detailed results from this run are included as Appendix~\ref{app:linktypes}.  On English, \input{figure/allowed_labels_both.tex}of \input{figure/allowed_labels_total.tex}link {\em types} allowed both directions, and only $\sum_{ij} s_{ij} = \input{figure/label_token_disallowed}$ of \input{figure/label_token_total}link {\em tokens} required a disallowed direction via slack.
\input{figure/conll_analysis_sentences_multiheaded}of the English sentences and 0.15\% of the Russian sentences had at least one multiheaded word.
